---
title: "Cases"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gt)
```

## Clinical Cases

During residency, training, and further clinical practice, I've given conferences based on clinical cases of interest. I have produced or created them here.

### Cardiology Fellowship

An interesting case of [restrictive cardiomyopathy](https://asshah4.github.io/patient-log/cases/12-14-20_biatrial-enlargement/biatrial-enlargement.html), including workup and consideration of alternative etiologies.

## Clinical Volume

As part of both residency and fellowship training, clinical volumes are important as they correlate with clinical aptitude. 

```{r, echo = FALSE}
# Main log
log <- readxl::read_excel("log.xlsx") %>%
	janitor::clean_names() %>%
	mutate(date = as.Date(date))

# Columns = site | mrn | date | dx1:3 | procedure | location | notes

# Obtain summaries of types
what <- unique(log$procedure)
where <- unique(log$location)

# Some procedures need specific modifiers, located in the location name
	# Caths -> needs modifier for site
	# TTE -> needs modifier for bedside or not
	# TEE -> needs modifier for if bedside or not
	# EPS -> needs modifier for type
	# DCCV -> modifier for joules, not really needed
	# TVP -> modifier
	# AL/CVL -> lines with locations in modifier

procedures <- c("RHC", "LHC", "PCI", "TEE", "TTE", "DCCV", "stress", "MRI", "TVP", "device interrogation", "pacemaker/ICD", "EPS", "pericardiocentesis")

# Summarize
log %>%
	filter(procedure %in% procedures & !is.na(location)) %>%
	group_by(procedure) %>%
	count() %>%
	ungroup() %>%
	gt(rowname_col = "procedure") %>%
	tab_header(
		title = "Procedure Log",
		subtitle = "UIC Cardiology Fellowship"
	) %>%
	tab_source_note(
		source_note = "PGY-4, July 2020 to December 2020"
	) %>%
	tab_stubhead("Procedures") %>%
	as_raw_html()
```



