---
title: "Part 2: Typical AVNRT"
subtitle: Clinical Electrophysiology Conference
author: Anish S. Shah, MD, MS
institute: Division of Cardiology, University of Illinois at Chicago 
date: December 08, 2022
date-format: long
engine: knitr
format:
  revealjs:
    transition: fade
    transition-speed: fast
    slide-number: true
    incremental: false
revealjs-plugins:
  - attribution
jupyter: python3
---

```{r}
#| echo: false
library(tidyverse)
library(coraline)
library(rhythm)
library(sf)
library(scales)
library(ggsci)

blue <- pal_material("blue", reverse = TRUE)(9)
orange <- pal_material("yellow", reverse = TRUE)(9)
red <- pal_material("pink", reverse = TRUE)(9)
green <- pal_material("teal", reverse = TRUE)(9)
grey <- pal_material("blue-grey", reverse = TRUE)(9)

find_project_folder <- function() {
	x <- sessionInfo()$running
	if (grepl("mac", x)) {
		file.path("/Users", "asshah4", "projects")
	} else if (grepl("Windows", x)) {
		file.path("C:/Users", "asshah4", "projects")
	}
}

loc <- file.path(find_project_folder(), "clinical", "lectures", "avnrt-series")
```

## Objectives

1. Understand the concepts of dual node physiology
1. Know the requirements for [typical AVNRT]{.orange}
1. Evaluate the response of [standard EP maneuvers]{.green} in [typical AVNRT]{.orange}

## {.smaller}

| Abbr. | Abbreviation |
|:--- |:---- |
| DAD | delayed after-depolarization |
| EAD | early after-depolarization | 
| APD | atrial premature depolarization | 
| VPD | ventricular premature depolarization | 

# Typical AVNRT

## {background-image="resources/josephsen-avnrt-schematic.png" background-size="contain"}

## Criteria

- Initiation and termination by APD/VPD during AV nodal Wenckebach cycles
- Dual AV nodal physiology (differential refractory curves during APD)
- Initiation dependent on critical AH interval during slow pathway conduction
- Retrograde atrial activation with variable VA activation in Triangle of Koch
- Initiated, terminated, or reset without atrial activation

::: aside
[Slow-fast AVNRT has atrial activation close to QRS complex, such that AH/HA > 1]{.grey}
:::

## Differential

- Atypical AVNRT
- Non-reentrant junctional tachycardia (junctional ectopic tachycardia)
- Non-paroyxsmal junctional tachycardia (d/t digitalis-induced DADs)
- Dual AV nodal tachycardia (repetitive retrograde concealment or "linking" phenomenon)
- Atrial tachycardia _always a possibility_

## Evaluation

1. Mode of initiation of tachycardia
1. Atrial activation sequence during tachycardia
1. Influence of bundle branch block on conduction and cycle length during tachycardia
1. Requirement of atria/ventricle for initiation and maintenance of tachcyardia
1. Effect of atrial/ventricular stiulation during tachycardia
1. Effect of drugs or physiological maneuvers on tachycardia

# Electrophysiology Study

## {background-image="tmf_data/ecg-case-nsr.png" background-size="contain"}

## {background-image="tmf_data/ecg-case-svt-new.png" background-size="contain"}

---

::: {.columns}

::: {.column width="50%"}
__Sinus Rhythm__

- Normal P and R axis
- RR = 900
- PP = 900
- QRS = 80
- P = 120
- PR = 160
- QT = 440

:::

::: {.column width="50%"}
__SVT__

- Suspected retro-grade P 
- RR = 350
- QRS = 70
- PR = 300  

::: {.fragment .highlight-red}
- RP = 40
:::

:::

:::

---

::: {.columns} 

::: {.column width="60%"}
- CS: decapolar catheter
- His: quadrapolar catheter
- RV: quadrapolar catheter
:::

::: {.column width="40%"}

```{r}
#| label: sinus rhythm from surface
#| cache: true
nsr <- 
	read_lspro(file.path(loc, "tmf_data/lsp-nsr-surface.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = nsr,
	channels = c("I", "II", "III" , "AVR", "AVL", "AVF", paste0("V", 1:6)),
	time_frame = c(1, 2)
)
```
:::

:::

## SVT features prior to diagnostic pacing maneuvers

For typical AVNRT, there are some findings to help eliminate options.

1. VA Relationship: any pattern, but most commonly V=A and V<A
1. VA Interval: VA &le; 70
1. Atrial Activation Sequence: concentric
1. Spontaneous Termination: end either in A or V response
1. VA Increase with BBB: no

---

```{r}
#| label: continuous tach prior to pacing
#| cache: true
tach <- 
	read_lspro(file.path(loc, "tmf_data/lsp-avnrt-ongoing.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = tach,
	channels = c("I", "CS", "HIS", "RV")
)
```

## Tachycardia initiation

- Tachycardia start:
	- APD that [blocks the fast pathway]{.blue}?
	- VPD that blocks retrograde?
- Activation sequence changes:
	- Atrial activation is concentric, eccentric, high-to-low? 
	- Are the ventricles and atria activated simultaneously?

---

```{r}
#| label: tach initiation
#| cache: true
tach_start <- 
	read_lspro(file.path(loc, "tmf_data/lsp-tach-initiation.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = tach_start,
	channels = c("I", "CS", "RV", "HIS D", "HIS M"),
	annotation_channel = "I",
	intervals = TRUE
)
```

---

```{r}
#| label: tach zoom to APD
#| cache: true
ggm(
	data = tach_start,
	channels = c("I", "CS", "RV", "HIS D", "HIS M"),
	time_frame = c(1.0, 3.0),
	annotation_channel = "CS 1-2",
	intervals = TRUE
)
```

## Dual AV Node Physiology

---

```{r}
#| label: cs pacing 800
#| cache: true
cs_s1_800_dec <-
	read_lspro(file.path(loc, "tmf_data/lsp-cs-pacing-800.txt")) |>
	{
		\(.x) melt_egm(.x$header, .x$signal, format = "lspro")
	}()

ggm(
	data = cs_s1_800_dec,
	channels = c("I", "CS", "HIS"),
	annotation_channel = "CS 9-10",
	intervals = TRUE
)
```

---

```{r}
#| label: cs pacing 700
#| cache: true
cs_s1_700_dec <-
	read_lspro(file.path(loc, "tmf_data/lsp-cs-pace-decremental-700ms.txt")) |>
	{
		\(.x) melt_egm(.x$header, .x$signal, format = "lspro")
	}()
ggm(
	data = cs_s1_700_dec,
	channels = c("I", "CS", "HIS"),
	annotation_channel = "CS 9-10",
	intervals = TRUE
)
```

---

```{r}
#| label: cs pacing 640
#| cache: true
cs_s1_640_dec <-
	read_lspro(file.path(loc, "tmf_data/lsp-cs-pace-decremental-640ms.txt")) |>
	{
		\(.x) melt_egm(.x$header, .x$signal, format = "lspro")
	}()

ggm(
	data = cs_s1_640_dec,
	channels = c("I", "CS", "HIS"),
	annotation_channel = "CS 9-10",
	intervals = TRUE
)
```

---

```{r}
#| label: cs pacing 400 with jump
#| cache: true
cs_s1_400_jump <-
	read_lspro(file.path(loc, "tmf_data/lsp-cs-pace-decremental-400ms-jump.txt")) |>
	{
		\(.x) melt_egm(.x$header, .x$signal, format = "lspro")
	}()

ggm(
	data = cs_s1_400_jump,
	channels = c("I", "CS", "HIS"),
	annotation_channel = "CS 9-10",
	intervals = TRUE
)
```

## Entrainment and pacing maneuvers

---

```{r}
#| label: cs entrainment
#| cache: true
cs_entrain <- 
	read_lspro(file.path(loc, "tmf_data/lsp-cs-entrainment.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = cs_entrain,
	channels = c("I", "CS", "HIS", "RV"),
	annotation_channel = "I",
	intervals = TRUE
)
```

---

```{r}
#| label: cs s1 entrained at attempted at 500
#| cache: true
cs_s1_500 <- 
	read_lspro(file.path(loc, "tmf_data/lsp-s1-500ms.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = cs_s1_500,
	channels = c("I", "CS", "HIS", "RV"),
	annotation_channel = "I",
	intervals = TRUE
)
```

---

```{r}
#| label: cs s1 entrained at 300
#| cache: true
cs_s1_300_entrain <- 
	read_lspro(file.path(loc, "tmf_data/lsp-entrainment-s1-300ms.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = cs_s1_300_entrain,
	channels = c("I", "CS", "HIS", "RV"),
	annotation_channel = "I",
	intervals = TRUE
)
```

---

```{r}
#| label: cs s2 breaks
#| cache: true
cs_s2_breaks <- 
	read_lspro(file.path(loc, "tmf_data/lsp-s2-breaks-rhythm.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = cs_s2_breaks,
	channels = c("I", "CS", "HIS", "RV"),
	annotation_channel = "I",
	intervals = TRUE
)
```

---

```{r}
#| label: cs bursts into afib
#| cache: true
cs_burst_af <- 
	read_lspro(file.path(loc, "tmf_data/lsp-burst-into-af.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = cs_burst_af,
	channels = c("I", "CS", "HIS", "RV"),
	annotation_channel = "I",
	intervals = TRUE
)
```

## Ruling out other mechanisms

---

```{r}
#| label: his refractory pvc
#| cache: true
his_pvc <- 
	read_lspro(file.path(loc, "tmf_data/lsp-his-refractory-pvc-success.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = his_pvc,
	channels = c("I", "CS", "HIS", "RV"),
	annotation_channel = "I",
	intervals = TRUE
)
```

---

```{r}
#| label: parahisian pacing
#| cache: true
parahis <- 
	read_lspro(file.path(loc, "tmf_data/lsp-parahisian-pacing.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = parahis,
	channels = c("I", "CS", "HIS", "RV"),
	annotation_channel = "I",
	intervals = TRUE
)
```

---

```{r}
#| label: avn erp
#| cache: true
avn_erp <- 
	read_lspro(file.path(loc, "tmf_data/lsp-avn-erp-s1-600ms-s2-220ms.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = avn_erp,
	channels = c("I", "CS", "HIS", "RV")
)
```

---


```{r}
#| label: post ablation avn erp
#| cache: true
abl_avn_erp <- 
	read_lspro(file.path(loc, "tmf_data/lsp-post-ablation-erp.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = abl_avn_erp,
	channels = c("I", "CS", "HIS", "RV")
)
```

---

```{r}
#| label: post ablation s4
#| cache: true
cs_s4_no_tach <- 
	read_lspro(file.path(loc, "tmf_data/lsp-s4-stim-no-tach.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = cs_s4_no_tach,
	channels = c("I", "CS", "HIS", "RV"),
	annotation_channel = "CS 9-10",
	intervals = TRUE
)
```

---

```{r}
#| label: pvc
#| cache: true
pvc <- 
	read_lspro(file.path(loc, "tmf_data/lsp-single-pvc.txt")) |>
	{\(.x) melt_egm(.x$header, .x$signal, format = "lspro")}()

ggm(
	data = cs_s1_500,
	channels = c("I", "CS", "HIS", "RV"),
	annotation_channel = "I",
	intervals = TRUE
)
```

# References

## {.smaller}

::: {#refs}
:::